\textbf{Benchmark voor latency bij edge-devices.}


There is a large diversity of subjects in which the duration of receiving results must remain within certain time limits. Due to this, a consideration is often made between cloud and edge computing. In the cloud powerful and fast hardware can be used. However, a significant delay arises when sending data over the internet. Executing programs in the edge does not suffer from these delays. This can be advantageous with latency sensitive applications like autonomous driving of vehicles.

% Eerste paragraaf: waarover gaat de scriptie, geef een eenvoudige beschrijving van de doelen en methodes
This thesis discusses a benchmark of three different edge-devices and a regular computer. This benchmark offers information about latency and processor-performance of each device. This will deliver more insight when making a cost-benefit analysis. The examined devices within this thesis are devices like the Google Coral Dev who consists of a CPU and TPU and the Raspberry Pi who only disposes only of a CPU. Also, a Nvidia Jetson Nano and a Personal Computer is used who both contain a CPU and GPU.

% Tweede paragraaf: geef uitleg over de scriptiestructuur en vertel iets over de inhoud
To obtain a representative benchmark it is necessary to test different programs in an identical way. The programs that will be tested will be divided over the category's regression and classification. The data derived from the benchmark will consist of the latency and the processor usage from running each program. These will be reworked and normalised to make an analysis easier. This will include accounting for factors like price, clock speed and energy consumption.

% Derde paragraaf: het besluit, met een kort overzicht van de resultaten
From the results a clear difference can be derived from the different edge devices. The Nvidia Jetson Nano proves to have the most potential. This device achieves the lowest latency for all the applied programs. The results show as well that the Coral Dev is more energy efficient. When executing the same program on different devices, the Coral Dev will consume the least amount of energy.


\underline{Keywords:} benchmark, edge-devices, latency, Jetson Nano, Coral Dev, Raspberry Pi